Figures and tables for paper

### 2021-10-29 analysis/04_figs-tables.Rmd
partially complete contrasts

# Reference Level = Friendly relationship with government
#  contrasts <- tibble(
#    under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
#    criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
#    )

# Plot the contrasts
# contrasts %>%
#  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
# ggsave(
#  "contrasts_hypothesis02b.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
# )
```

@@

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# contrasts <- tibble(
#  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
#  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
#  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
#  )

# Plot the contrasts
#contrasts %>%
# pivot_longer(environment:refugee_relief, names_to = "level", values_to = "Gamma") %>% 
#  ggplot(aes(x = Gamma, y = level)) +
#  stat_halfeye(.width = .95) +
#  geom_vline(xintercept = 0, color = "grey") +
#  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
#ggsave(
# "contrasts_hypothesis03b.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)
```

@@

# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations
#contrasts <- tibble(
#  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
#  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
#  )

# Save plot
#ggsave(
#  "contrasts_hypothesis04b.png",
#  path = here::here("analysis", "output", "figures"),
#  width = 12,
#  height = 6,
#  units = "in"
#)

>>>>

# Reference Level = Friendly relationship with government
intib <- read_rds(
    here::here("analysis", "output", "posterior_draws", "interactions.rds")
  )
contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = oxfam_criticized - amnesty_criticized,
    oxfam_greenpeace_criticized = oxfam_criticized - greenpeace_criticized,
    red_cross_amnesty_criticized = red_cross_criticized - amnesty_criticized,
    red_cross_greenpeace_criticized = red_cross_criticized - greenpeace_criticized,
    oxfam_amnesty_crackdown = oxfam_crackdown - amnesty_crackdown,
    oxfam_greenpeace_crackdown = oxfam_crackdown - greenpeace_crackdown,
    red_cross_amnesty_crackdown = red_cross_crackdown - amnesty_crackdown,
    red_cross_greenpeace_crackdown = red_cross_crackdown - greenpeace_crackdown
  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis02b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
 )
```

@@

# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
contrasts_int <- tibble(
  criticized_environment = intib %>% filter(i == 22) %>% select(Gamma) %>% pull(),
  criticized_humanrights = intib %>% filter(i == 23) %>% select(Gamma) %>% pull(),
  criticized_refugee = intib %>% filter(i == 24) %>% select(Gamma) %>% pull(),
  crackdown_environment = intib %>% filter(i == 25) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = intib %>% filter(i == 26) %>% select(Gamma) %>% pull(),
  crackdown_refugee = intib %>% filter(i == 27) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  criticized_refugee_environment = criticized_refugee - criticized_environment,
  criticized_refugee_humanrights = criticized_refugee - criticized_humanrights,
  crackdown_refugee_environment = crackdown_refugee - crackdown_environment,
  crackdown_refugee_humanrights = crackdown_refugee - crackdown_humanrights
  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_refugee_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
 "contrasts_hypothesis03b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

@@

# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations
contrasts_int <- tibble(
  criticized_wealthydonors = intib %>% filter(i == 28) %>% select(Gamma) %>% pull(),
  criticized_grants = intib %>% filter(i == 29) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = intib %>% filter(i == 30) %>% select(Gamma) %>% pull(),
  crackdown_grants = intib %>% filter(i == 31) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  criticized_wealthydonors_grants = criticized_wealthydonors - criticized_grants,
  crackdown_wealthydonors_grants = crackdown_wealthydonors - crackdown_grants,
  )
# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_wealthydonors_grants:crackdown_wealthydonors_grants, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis04b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
